Classical mechanics as the high-entropy limit \\ of quantum mechanics

### 2025-12-02 Articles/2024-ClassicalLimit/classicalLimitArticle.tex
Added various references to the bib file and text

Coherence is probably one of the direct and most important properties. It has been shown that coherence can be maintained over long distances and among a large number of constituents, meaning that quantum systems are not necessarily small or made of few components. However, it is also established how coherence can be quickly lost through interaction with the environment, through decoherence~\cite{RevModPhys.75.715, SCHLOSSHAUER20191}. Since decoherence increases the entropy of the system, it represents one mechanism to reach the high-entropy limit. This is in line with our result.

@@

It should be clear that this investigation does not exhaust all possible insights and links to the now vast literature on open quantum systems, quantum statistical mechanics, quantum information, quantum sensing and so on. For example, entropy and entropy increase play a role in several approaches: coarse graining(\href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.99.180403}{CITE}), decoherence(CITE 1 2 5 ), stochastic processes (CITE \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.129.050401}{Quantum Fokker-Planck Master Equation for Continuous Feedback Control}) and information-theoretic and resource-theoretic approaches (cite 3 4 6 7) to name a few. On a more technical level, since both the Husimi Q and the Wigner function converge to the classical distribution, the Wehrl entropy, which is the Shannon entropy calculated on the Husimi Q, will converge to the Gibbs entropy. One may ask, then, whether a high Wehrl entropy is already an indicator of classicality, and, if so, it would give another insight as to why the anti-normal ordering is important. Lastly, the role of entropic ideas is well established in historic literature. It would not be possible here to comment on all of them, and the more we mention, the more the omitted mentions are felt. Therefore we had to only explore the most important elements to establish the limit mathematically and under the smallest conceptual footprint, also as to not distract from the main point of the paper.

>>>>

Coherence is probably one of the direct and most important properties. It has been shown that coherence can be maintained over long distances and among a large number of constituents, meaning that quantum systems are not necessarily small or made of few components. However, it is also established how coherence can be quickly lost through interaction with the environment, through decoherence~\cite{Zurek_RevModPhys.75.715, SCHLOSSHAUER20191}. Since decoherence increases the entropy of the system, it represents one mechanism to reach the high-entropy limit. This is in line with our result.

@@

It should be clear that this investigation does not exhaust all possible insights and links to the now vast literature on open quantum systems, quantum statistical mechanics, quantum information, quantum sensing and so on. For example, entropy and entropy increase play a role in several approaches: coarse-grained measurement (e.g.~Refs.~\cite{Kofler2007,bibak2025classicallimitquantummechanics}), decoherence (e.g.~Refs.~\cite{Zurek_RevModPhys.75.715,DecoherenceBook2003,SCHLOSSHAUER20191}), stochastic processes (e.g.~Refs.~\cite{carmichael2013statistical,QuantumStochasticReview,QuantumFokkerPlanck2022}) and information-theoretic and resource-theoretic approaches (e.g.~Refs.~\cite{Goold_2016,QuantumResourceReview2019,Shiraishi2025}) to name a few. On a more technical level, since both the Husimi Q and the Wigner function converge to the classical distribution, the Wehrl entropy, which is the Shannon entropy calculated on the Husimi Q, will converge to the Gibbs entropy. One may ask, then, whether a high Wehrl entropy~\cite{Wehrl1979} is already an indicator of classicality, and, if so, it would give another insight as to why the anti-normal ordering is important. Lastly, the role of entropic ideas is well established in historic literature. It would not be possible here to comment on all of them, and the more we mention, the more the omitted mentions are felt. Therefore we only explore the most important elements to establish the limit mathematically and under the smallest conceptual footprint, also as to not distract from the main point of the paper.
